Distinction Centrality Analysis

### 2025-09-20 analysis.qmd
poli plots

>>>>

## Political Data

```{r Loading TestPolitical Data}
   poli1 <- as.matrix(read.csv(here("Data", "poli1.csv")))
   poli1 <- graph_from_edgelist(poli1, directed = FALSE)
   poli2 <- as.matrix(read.csv(here("Data", "poli2.csv")))
   poli2 <- graph_from_edgelist(poli2, directed = FALSE)
   poli3 <- as.matrix(read.csv(here("Data", "poli3.csv")))
   poli3 <- graph_from_edgelist(poli3, directed = FALSE)
   poli4 <- as.matrix(read.csv(here("Data", "poli4.csv")))
   poli4 <- graph_from_edgelist(poli4, directed = FALSE)
   png(here("Plots", "poli1.png"), height = 600, width = 1000)
   plot.graph.norm(poli1, l = "auto")
   dev.off()
   png(here("Plots", "poli2.png"), height = 600, width = 1000)
   plot.graph.norm(poli2, l = "auto")
   dev.off()
   png(here("Plots", "poli3.png"), height = 600, width = 1000)
   plot.graph.norm(poli3, l = "auto")
   dev.off()
   png(here("Plots", "poli4.png"), height = 600, width = 1000)
   plot.graph.norm(poli4, l = "auto")
   dev.off()
```
